---
title: "Calibration scenarios comparison"
author: "FMJ Bulot"
date: "`r format(Sys.time(), '%d %B, %Y, %H:%M')`"
knit: (function(inputFile, encoding) { 
      out_dir <- '../../docs/';
      rmarkdown::render(inputFile,
                        encoding=encoding, 
                        output_file=file.path(dirname(inputFile), out_dir, 'calibration_scenarios_comparison.html'))})
output:
  html_document:
    df_print: paged
    code_folding: hide
    toc: true
    toc_depth: 2
    toc_float:
      collapsed: false
editor_options: 
  markdown: 
    wrap: 80
---

This notebook explores the results from the scripts in the folder
`calibration_scenarios_Xweeks_Xmonths`. Note that these scripts require a lot
of computational time and a lost of space to store the results of the 
different calibration (about 174Gb).
For each calibration scenario, the script has been divided into several files 
so they can be ran in parallel (for instance
using background jobs, launched from the root directory) to speed up the 
calculations.

These represents the different calibration scenarios presented in the paper: - 1
week of pre-deployment calibration, 2 months of evaluation, 1 week of
post-deployment calibration - 2 weeks of pre-deployment calibration, 2 months of
evaluation, 2 weeks of post-deployment calibration - 2 weeks of pre-deployment
calibration, 4 months of evaluation, 2 weeks of post-deployment calibration - 2
weeks of pre-deployment calibration, 6 months of evaluation, 2 weeks of
post-deployment calibration - 1 week of pre-deployment calibration, 2 months of
evaluation - 2 weeks of pre-deployment calibration, 2 months of evaluation - 4
weeks of pre-deployment calibration, 2 months of evaluation

```{r}

source("utilities/utilities.R")
source("utilities/nested_models.r")
source("utilities/variables.r")

require(tidytext)
```

```{r}

input_folder <-
  paste0(here::here(),
         "/output/calibration/scenarios/calibration_scenarios_comparison/")

res <-
  readRDS(paste0(input_folder, "res_calibration_scenario_comparison.rds"))
res_bus <-
  readRDS(paste0(input_folder, "res_bus_calibration_scenario_comparison.rds"))

```

```{r}



res$method <-
  fct_recode(
    res$method,
    `Koehler_mass+LR` = "koehlermasslr",
    `Koehler_mass+OLS` = "koehlermassols",
    `Koehler_size+LR` = "koehlersizelr",
    `Koehler_size+OLS` =  "koehlersizeols",
    `Laulainen+LR` = "laulainenlr",
    `Laulainen+OLS` = "laulainenols",
    `MLR_part.` =  "lmpart",
    `MLR_part.+RH` =   "lmpartrh",
    `LR` = "lr",
    `MLR_RH` = "mlr1" ,
    `OLS` =  "ols",
    `RLM` = "rlmhuber",
    `RLM_part.+RH`  = "rlmpartrh",
    `RLM+RH` =      "rlmrh",
    `RLM_part.` = "rlmpart"
  )
res$method <-
  fct_relevel(
    res$method,
    "Initial",
    "OLS",
    "LR",
    "MLR_RH",
    "MLR_part.",
    "MLR_part.+RH",
    "RLM",
    "RLM+RH",
    "RLM_part.",
    "RLM_part.+RH",
    "Koehler_mass+LR",
    "Koehler_mass+OLS",
    "Koehler_size+LR",
    "Koehler_size+OLS",
    "Laulainen+LR",
    "Laulainen+OLS"
  )

res_bus$method <-
  fct_recode(
    res_bus$method,
    `Koehler_mass+LR` = "koehlermasslr",
    `Koehler_mass+OLS` = "koehlermassols",
    `Koehler_size+LR` = "koehlersizelr",
    `Koehler_size+OLS` =  "koehlersizeols",
    `Laulainen+LR` = "laulainenlr",
    `Laulainen+OLS` = "laulainenols",
    `MLR_part.` =  "lmpart",
    `MLR_part.+RH` =   "lmpartrh",
    `LR` = "lr",
    `MLR_RH` = "mlr1" ,
    `OLS` =  "ols",
    `RLM` = "rlmhuber",
    `RLM_part.+RH`  = "rlmpartrh",
    `RLM+RH` =      "rlmrh",
    `RLM_part.` = "rlmpart"
  )
res_bus$method <-
  fct_relevel(
    res_bus$method,
    "Initial",
    "OLS",
    "LR",
    "MLR_RH",
    "MLR_part.",
    "MLR_part.+RH",
    "RLM",
    "RLM+RH",
    "RLM_part.",
    "RLM_part.+RH",
    "Koehler_mass+LR",
    "Koehler_mass+OLS",
    "Koehler_size+LR",
    "Koehler_size+OLS",
    "Laulainen+LR",
    "Laulainen+OLS"
  )

res$scenario_type <-
  fct_recode(
    res$scenario_type,
    `1w8w1w` = "1w2m1w",
    `2w8w` = "2w",
    `2w8w2w` = "2w2m2w",
    `4w8w` =  "4w",
    `2w16w2w` = "2w4m2w"
  )

res$scenario_type <-
  fct_relevel(res$scenario_type,
              "2w8w",
              "4w8w",
              "1w8w1w",
              "2w8w2w",
              "2w16w2w",
              "2w24w2w")

res_bus$scenario_type <-
  fct_recode(
    res_bus$scenario_type,
    `1w8w1w` = "1w2m1w",
    `2w8w` = "2w",
    `2w8w2w` = "2w2m2w",
    `4w8w` =  "4w" ,
    `2w16w2w` = "2w4m2w"
  )

res_bus$scenario_type <-
  fct_relevel(res_bus$scenario_type,
              "2w8w",
              "4w8w",
              "1w8w1w",
              "2w8w2w",
              "2w16w2w",
              "2w24w2w")

res <- res[!grepl("N2", res$sensor),]
res_bus <- res_bus[!grepl("N2", res_bus$combination),]

```

# Filter out techniques discarded by robust selection

```{r}


res <-
  res[!(
    res$method %in% c(
      "Koehler_mass+LR",
      "Koehler_mass+OLS",
      "Koehler_size+LR",
      "Koehler_size+OLS",
      "Laulainen+LR",
      "Laulainen+OLS",
      "koehlermass",
      "koehlersize",
      "laulainen"
    )
  ),] %>%
  dplyr::mutate(sensor_type = ifelse(grepl("SPS", sensor), "SPS30", "PMS5003"))

res_bus <-
  res_bus[!(
    res_bus$method %in% c(
      "Koehler_mass+LR",
      "Koehler_mass+OLS",
      "Koehler_size+LR",
      "Koehler_size+OLS",
      "Laulainen+LR",
      "Laulainen+OLS",
      "koehlermass",
      "koehlersize",
      "laulainen"
    )
  ),] %>%
  dplyr::mutate(sensor_type = ifelse(grepl("SPS", combination), "SPS30", "PMS5003")) 

```

# Results

## RMSE and Between Unit Uncertainty

```{r}


p_rmse <- res %>%
  dplyr::filter(type == "Full") %>%
  dplyr::filter(dataset_type == "cal") %>%
  ggplot(aes(x = method, y = RMSE, colour = scenario_type)) +
  stat_boxplot(geom = "errorbar") +
  geom_boxplot(
    fatten = 0.8,
    outlier.size = 0.3,
    outlier.alpha = 0.5,
    lwd = 0.2
  ) +
  custom_theme +
  theme(axis.text.x = element_text(
    angle = 90,
    hjust = 0.95,
    vjust = 0.2
  )) +
  facet_wrap( ~ sensor_type, ncol = 2, scales = "free_y") +
  xlab("Calibration method") +
  ylab(quickText("RMSE (ug/m3)")) +
  ylim(c(0, quantile(res$RMSE, probs = 0.9)))
#p_rmse




p_bus <- res_bus %>%
  dplyr::filter(type == "Full") %>%
  dplyr::filter(dataset_type == "cal") %>%
  ggplot(aes(
    x = method,
    y = usb,
    colour = scenario_type
  )) +
  stat_boxplot(geom = "errorbar") +
  geom_boxplot(
    fatten = 0.8,
    outlier.size = 0.3,
    outlier.alpha = 0.5,
    lwd = 0.2
  ) +
  #geom_line(data = table_res, aes(x=method,y=mean_RMSE, colour=sensor))+
  # ggtitle("Calibration - PMS - Scenarios comparison") +
  custom_theme +
  theme(axis.text.x = element_text(
    angle = 90,
    hjust = 0.95,
    vjust = 0.2
  )) +
  facet_wrap( ~ sensor_type, ncol = 2, scales = "free_y") +
  xlab("Calibration method") +
  ylab(quickText("Between unit uncertainty (ug/m3)"))
#p_bus


legend <- get_legend(# create some space to the left of the legend
  p_rmse +
    guides(color = guide_legend(ncol = 1, title = "Sensors")) +
    #theme(legend.position = "bottom") +
    theme(legend.box.margin = margin(0, 0, 0, 0)))

pg <-
  plot_grid(
    p_rmse + xlab(NULL) + guides(x = "none") + theme(legend.position = "none"),
    p_bus + theme(legend.position = "none"),
    nrow = 2,
    labels = c("(a)", "(b)"),
    label_y = c(0.1, 0.1)
  )





pg_l <- plot_grid(pg,
                  legend,
                  ncol = 2,
                  rel_widths  = c(0.8, 0.2))
pg_l
#ggsave2(plot = pg_l,filename=paste0(output_plot_folder, "comparison_scenarios.svg"),
#    height = 140, units = "mm")


```

## On RLM_part.+RH only

In this section we only focus on the four methods that performed both during the 
robust method selection ((presented in in [Calibration 2 weeks 40
days](calibration_2weeks_40days.html)), with a special focus on RLM_part.+RH for
clarity in the graph.


```{r}


p_rmse <- res %>%
  dplyr::filter(type == "Full") %>%
  dplyr::filter(dataset_type == "cal") %>%
  dplyr::filter(method %in% c("RLM_part.+RH", "RLM_part.", "MLR_part.", "MLR_part.+RH")) %>%
  ggplot(aes(
    x = reorder_within(scenario_type, RMSE, sensor_type, median),
    y = RMSE,
    colour = method
  )) +
  stat_boxplot(geom = "errorbar") +
  geom_boxplot(
    fatten = 0.8,
    outlier.size = 0.3,
    outlier.alpha = 0.5,
    lwd = 0.2
  ) +
  #geom_line(data = table_res, aes(x=method,y=mean_RMSE, colour=sensor))+
  # ggtitle("Calibration - PMS - Scenarios comparison") +
  custom_theme +
  theme(axis.text.x = element_text(
    angle = 90,
    hjust = 0.95,
    vjust = 0.2
  )) +
  facet_wrap( ~ sensor_type, ncol = 2, scales = "free") +
  xlab("Calibration method") +
  ylab(quickText("RMSE (ug/m3)")) +
  ylim(c(0, quantile(res$RMSE, probs = 0.9)))
p_rmse

p_rmse <- res %>%
  dplyr::filter(type == "Full") %>%
  dplyr::filter(dataset_type == "cal") %>%
  dplyr::filter(method %in% c("RLM_part.+RH", "RLM_part.", "MLR_part.", "MLR_part.+RH")) %>%
  ggplot(aes(
    x = reorder_within(method, RMSE, sensor_type, median),
    y = RMSE,
    colour = scenario_type
  )) +
  stat_boxplot(geom = "errorbar") +
  geom_boxplot(
    fatten = 0.8,
    outlier.size = 0.3,
    outlier.alpha = 0.5,
    lwd = 0.2
  ) +
  #geom_line(data = table_res, aes(x=method,y=mean_RMSE, colour=sensor))+
  # ggtitle("Calibration - PMS - Scenarios comparison") +
  custom_theme +
  theme(axis.text.x = element_text(
    angle = 90,
    hjust = 0.95,
    vjust = 0.2
  )) +
  facet_wrap( ~ sensor_type, ncol = 2, scales = "free") +
  xlab("Calibration method") +
  ylab(quickText("RMSE (ug/m3)")) +
  ylim(c(0, quantile(res$RMSE, probs = 0.9)))
p_rmse





```

```{r}


median_IQR <- function(x) {
  data.frame(y = quantile(x)[4],
             label = round2(quantile(x)[4] - quantile(x)[2], n = 1))
}


p_rmse <- res %>%
  dplyr::filter(type == "Full") %>%
  dplyr::filter(dataset_type == "cal") %>%
  dplyr::filter(method %in% c("RLM_part.+RH")) %>%
  ggplot(aes(x = sensor, y = RMSE, colour = scenario_type)) +
  stat_boxplot(geom = "errorbar") +
  geom_boxplot(
    fatten = 1,
    outlier.size = 0.3,
    outlier.alpha = 0.5,
    lwd = 0.2
  ) +
  #geom_line(data = table_res, aes(x=method,y=mean_RMSE, colour=sensor))+
  # ggtitle("Calibration - PMS - Scenarios comparison") +
  custom_theme +
  # theme(axis.text.x = element_text(angle = 90, hjust=0.95,vjust=0.2)) +
  facet_wrap( ~ sensor_type, nrow = 2, scales = "free") +
  xlab("Sensors") +
  ylab(quickText("RMSE (ug/m3)")) +
  #ylim(c(0,quantile(res$RMSE,probs = 0.9))) +
  stat_summary(
    geom = "text",
    fun.data = median_IQR,
    aes(group = scenario_type),
    size = 2,
    position = position_dodge(width = 0.75),
    vjust = -0.5,
    colour = "black"
  ) +
  theme(legend.position = "bottom") + guides(colour = guide_legend(nrow = 1)) +
  scale_y_continuous(limits = c(0, quantile(res$RMSE, probs = 0.9)),
                     minor_breaks = seq(0, 10, 0.2)) +
  labs(colour = "Scenarios")
p_rmse
ggsave2(
  plot = p_rmse,
  filename = paste0(
    PLOT_OUTPUT_FOLDER,
    "comparison_scenarios_rmse_RLMparRH.png"
  ),
  height = 200,
  units = "mm"
)
```

### Between unit uncertainty

```{r}


duplicated_cbn <-
  c(
    "PMS-63N3 - PMS-86N2",
    "PMS-65N4 - PMS-86N2",
    "PMS-75N3 - PMS-86N2",
    "PMS-91N4 - PMS-86N2",
    "SPS-19N4 - SPS-38N2",
    "SPS-21N4 - SPS-38N2",
    "SPS-36N3 - SPS-38N2",
    "SPS-41N3 - SPS-38N2"
  )

p_bus <- res_bus %>%
  dplyr::filter(type == "Full") %>%
  dplyr::filter(dataset_type == "cal") %>%
  dplyr::filter(method %in% c("RLM_part.+RH")) %>%
  dplyr::filter(!(combination %in% duplicated_cbn)) %>%
  ggplot(aes(
    x = str_remove_all(combination, "SPS-|PMS-") ,
    y = usb,
    colour = scenario_type
  )) +
  stat_boxplot(geom = "errorbar") +
  geom_boxplot(
    fatten = 0.8,
    outlier.size = 0.3,
    outlier.alpha = 0.5,
    lwd = 0.2
  ) +
  #geom_line(data = table_res, aes(x=method,y=mean_RMSE, colour=sensor))+
  # ggtitle("Calibration - PMS - Scenarios comparison") +
  custom_theme +
  theme(axis.text.x = element_text(
    angle = 90,
    hjust = 0.95,
    vjust = 0.2
  )) +
  facet_wrap( ~ sensor_type, nrow = 2, scales = "free") +
  xlab("Calibration method") +
  ylab(quickText("Between unit uncertainty (ug/m3)")) +
  stat_summary(
    geom = "text",
    fun =  ~ quantile(.x, probs = c(1, 2, 3) / 4),
    aes(group = scenario_type, label = sprintf("%1.1f", ..y..)),
    size = 2,
    position = position_dodge(width = 0.75),
    vjust = -0.5,
    colour = "black"
  ) +
  theme(legend.position = "bottom") + guides(colour = guide_legend(nrow = 1))
p_bus


p_bus <- res_bus %>%
  dplyr::filter(type == "Full") %>%
  dplyr::filter(dataset_type == "cal") %>%
  dplyr::filter(method %in% c("RLM_part.+RH")) %>%
  ggplot(aes(x = scenario_type , y = usb, colour = scenario_type)) +
  stat_boxplot(geom = "errorbar") +
  geom_boxplot(
    fatten = 0.8,
    outlier.size = 0.3,
    outlier.alpha = 0.5,
    lwd = 0.2
  ) +
  #geom_line(data = table_res, aes(x=method,y=mean_RMSE, colour=sensor))+
  # ggtitle("Calibration - PMS - Scenarios comparison") +
  custom_theme +
  theme(axis.text.x = element_text(
    angle = 90,
    hjust = 0.95,
    vjust = 0.2
  )) +
  facet_wrap( ~ sensor_type, nrow = 2, scales = "free") +
  xlab("Calibration method") +
  ylab(quickText("Between unit uncertainty (ug/m3)")) +
  stat_summary(
    geom = "text",
    fun =  ~ quantile(.x, probs = c(1, 2, 3) / 4),
    aes(group = scenario_type, label = sprintf("%1.1f", ..y..)),
    size = 2,
    position = position_dodge(width = 0.75),
    vjust = -0.5,
    colour = "black"
  )
p_bus


```

## Other metrics

```{r}



p_bias <- res %>%
  dplyr::filter(type == "Full") %>%
  dplyr::filter(dataset_type == "cal") %>%
  ggplot(aes(x = method, y = y__, colour = scenario_type)) +
  stat_boxplot(geom = "errorbar") +
  geom_boxplot(
    fatten = 0.8,
    outlier.size = 0.3,
    outlier.alpha = 0.5,
    lwd = 0.2
  ) +
  #geom_line(data = table_res, aes(x=method,y=mean_RMSE, colour=sensor))+
  # ggtitle("Calibration - PMS - Scenarios comparison") +
  custom_theme +
  theme(axis.text.x = element_text(
    angle = 90,
    hjust = 0.95,
    vjust = 0.2
  )) +
  facet_wrap( ~ sensor_type, ncol = 2, scales = "free_y") +
  xlab("Calibration method") +
  ylab(quickText("Bias (ug/m3)")) +
  ylim(c(0, quantile(res$y__, probs = 0.9)))
p_bias


p_U <- res %>%
  dplyr::filter(type == "Full") %>%
  dplyr::filter(dataset_type == "cal") %>%
  ggplot(aes(x = method, y = U, colour = scenario_type)) +
  stat_boxplot(geom = "errorbar") +
  geom_boxplot(
    fatten = 0.8,
    outlier.size = 0.3,
    outlier.alpha = 0.5,
    lwd = 0.2
  ) +
  #geom_line(data = table_res, aes(x=method,y=mean_RMSE, colour=sensor))+
  # ggtitle("Calibration - PMS - Scenarios comparison") +
  custom_theme +
  theme(axis.text.x = element_text(
    angle = 90,
    hjust = 0.95,
    vjust = 0.2
  )) +
  facet_wrap( ~ sensor_type, ncol = 2, scales = "free_y") +
  xlab("Calibration method") +
  ylab(quickText("Uncertainty USEPA (%)")) +
  ylim(c(0, quantile(res$U, probs = 0.9)))
p_U


p_cv <- res %>%
  dplyr::filter(type == "Full") %>%
  dplyr::filter(dataset_type == "cal") %>%
  ggplot(aes(x = method, y = cv, colour = scenario_type)) +
  stat_boxplot(geom = "errorbar") +
  geom_boxplot(
    fatten = 0.8,
    outlier.size = 0.3,
    outlier.alpha = 0.5,
    lwd = 0.2
  ) +
  #geom_line(data = table_res, aes(x=method,y=mean_RMSE, colour=sensor))+
  # ggtitle("Calibration - PMS - Scenarios comparison") +
  custom_theme +
  theme(axis.text.x = element_text(
    angle = 90,
    hjust = 0.95,
    vjust = 0.2
  )) +
  facet_wrap( ~ sensor_type, ncol = 2, scales = "free_y") +
  xlab("Calibration method") +
  ylab(quickText("CV (%)")) +
  ylim(c(0, quantile(res$cv, probs = 0.9)))
p_cv

p_ue <- res %>%
  dplyr::filter(type == "Full") %>%
  dplyr::filter(dataset_type == "cal") %>%
  ggplot(aes(x = method, y = expanded_uncertainty, colour = scenario_type)) +
  stat_boxplot(geom = "errorbar") +
  geom_boxplot(
    fatten = 0.8,
    outlier.size = 0.3,
    outlier.alpha = 0.5,
    lwd = 0.2
  ) +
  #geom_line(data = table_res, aes(x=method,y=mean_RMSE, colour=sensor))+
  # ggtitle("Calibration - PMS - Scenarios comparison") +
  custom_theme +
  theme(axis.text.x = element_text(
    angle = 90,
    hjust = 0.95,
    vjust = 0.2
  )) +
  facet_wrap( ~ sensor_type, ncol = 2, scales = "free_y") +
  xlab("Calibration method") +
  ylab(quickText("Expanded uncertainty (%)")) +
  ylim(c(0, quantile(
    res$expanded_uncertainty, probs = 0.9, na.rm = T
  )))
p_ue

p_r2 <- res %>%
  dplyr::filter(type == "Full") %>%
  dplyr::filter(dataset_type == "cal") %>%
  ggplot(aes(x = method, y = r2, colour = scenario_type)) +
  stat_boxplot(geom = "errorbar") +
  geom_boxplot(
    fatten = 0.8,
    outlier.size = 0.3,
    outlier.alpha = 0.5,
    lwd = 0.2
  ) +
  #geom_line(data = table_res, aes(x=method,y=mean_RMSE, colour=sensor))+
  # ggtitle("Calibration - PMS - Scenarios comparison") +
  custom_theme +
  theme(axis.text.x = element_text(
    angle = 90,
    hjust = 0.95,
    vjust = 0.2
  )) +
  facet_wrap( ~ sensor_type, ncol = 2, scales = "free_y") +
  xlab("Calibration method") +
  ylab(quickText("r2")) +
  ylim(c(0, quantile(
    res$r2, probs = 0.9, na.rm = T
  )))
p_r2



```


# Results in tables

```{r}


table_res <- res %>%
  dplyr::filter(grepl("PMS", sensor)) %>%
  dplyr::filter(type == "Full") %>%
  dplyr::filter(dataset_type == "cal") %>%
  group_by(scenario_type, sensor, method) %>%
  summarise(
    mean_RMSE = mean(RMSE, na.rm = T),
    quant25 = quantile(RMSE, probs = c(0.25), na.rm = T),
    quant75 = quantile(RMSE, probs = c(0.75), na.rm = T),
    median = median(RMSE, na.rm = T)
  ) %>%
  arrange(desc(mean_RMSE)) #%>%

table_res
table_res %>%
  write.csv(paste0(PLOT_OUTPUT_FOLDER, "table_res_pms.csv"), sep = "\tab")

res %>%
  dplyr::filter(grepl("PMS", sensor)) %>%
  dplyr::filter(type == "Full") %>%
  dplyr::filter(dataset_type == "cal") %>%
  group_by(scenario_type, sensor, method) %>%
  rstatix::get_summary_stats()

res_sensor_type <-  res %>%
  dplyr::filter(grepl("PMS", sensor)) %>%
  dplyr::filter(type == "Full") %>%
  dplyr::filter(dataset_type == "cal") %>%
  group_by(scenario_type, method, sensor_type) %>%
  rstatix::get_summary_stats()


table_res_sps <- res %>%
  dplyr::filter(grepl("SPS", sensor)) %>%
  dplyr::filter(type == "Full") %>%
  dplyr::filter(dataset_type == "cal") %>%
  group_by(scenario_type, sensor, method) %>%
  summarise(
    mean_RMSE = mean(RMSE, na.rm = T),
    quant25 = quantile(RMSE, probs = c(0.25), na.rm = T),
    quant75 = quantile(RMSE, probs = c(0.75), na.rm = T),
    median = median(RMSE, na.rm = T)
  ) %>%
  arrange(desc(mean_RMSE))
table_res_sps
table_res_sps %>%
  write.csv(paste0(PLOT_OUTPUT_FOLDER, "table_res_sps.csv"), sep = "\tab")


```
