---
title: "Calibration - 2 weeks - 40 days"
author: "FMJ Bulot (florentin.bulot@centraliens.net)"
date: "Last generated: `r format(Sys.time(), '%d %B, %Y, %H:%M')`"
output:
  html_document:
    df_print: paged
    code_folding: hide
    toc: true
    toc_depth: 2
    toc_float:
      collapsed: false
knit: (function(inputFile, encoding) { 
      out_dir <- '../docs';
      rmarkdown::render(inputFile,
                        encoding=encoding, 
                        output_file=file.path(dirname(inputFile), out_dir, 'evaluation_calibration_2weeks_40days.html'))})
editor_options: 
  markdown: 
    wrap: 80
---

```{r global_options, include=FALSE}
knitr::opts_chunk$set(fig.width=12, fig.height=8, fig.path='../Figs/evaluation_calibration_2weeks_40days/',warning=FALSE, message=FALSE)
```


This notebook presents the results from the scripts located in the subfolder
`2weeks_40days`. `calibration_2weeks_40days.r` performs the calibration on 
every possible subset of the dataset containing 2 weeks + 40 consecutive days.
The scripts has been split into several subscripts 
`calibration_2weeks_40days_[1-7].r` so they can be ran in parallel (for instance
using background jobs) to speed up the calculations.

The results are then aggregated by `calibration_2weeks_40days_agg.r` and stored
in `output/calibration/2weeks_40days_agg`.


```{r, message=F}

source("utilities/utilities.R")
source("utilities/nested_models.r")
source("utilities/variables.r")

input_folder <- paste0(here::here(),"/output/calibration/2weeks_40days_agg/")

```

```{r}

res <- readRDS(paste0(input_folder, "res_2weeks_40days_eu_agg.rds"))
res_bus <- readRDS(paste0(input_folder, "res_2weeks_40days_bus_agg.rds"))


filtered_out_methods <- c("koehlermass", "koehlersize", "laulainen", 
                                "Koehler_mass+OLS", "Koehler_size+OLS", 
                          "Laulainen+OLS")


res <- res[!(res$method %in% filtered_out_methods),]
res_bus <- res_bus[!(res_bus$method %in% filtered_out_methods),] 

res <- res[!grepl("N2", res$sensor), ]

res_bus <- res_bus[!grepl("N2", res_bus$combination), ]

```


# RMSE

```{r}
scaleFUN <-
  function(x)
    sprintf("%.1f", x) # to have only one digit for the axis

p_sps <- res %>%
  dplyr::filter(grepl("SPS", sensor)) %>%
  dplyr::filter(type == "Full") %>%
  dplyr::filter(dataset_type == "cal") %>%
  ggplot(aes(
    x = reorder(method, RMSE, median),
    y = RMSE,
    colour = sensor
  )) +
  stat_boxplot(geom = 'errorbar') +
  geom_boxplot(
    fatten = 0.8,
    outlier.size = 0.8,
    outlier.alpha = 0.5,
    lwd = 0.2
  ) +
  custom_theme +
  xlab("Calibration method") +
  ylab(quickText("RMSE (ug/m3)")) +
  labs(colour = "Sensors") +
  scale_y_continuous(labels = scaleFUN, limits = quantile(res$RMSE, c(0.1, 0.9))) +
  theme(axis.text.x = element_text(
    angle = 90,
    hjust = 0.95,
    vjust = 0.2
  ))

#p_sps

res %>%
  dplyr::filter(grepl("SPS", sensor)) %>%
  dplyr::filter(type == "Full") %>%
  dplyr::filter(dataset_type == "cal") %>%
  group_by(method) %>%
  summarise(
    mean  = mean(RMSE, na.rm = T),
    median  = median(RMSE, na.rm = T),
    q25 = quantile(RMSE, probs = c(0.25), na.rm = T),
    q75  = quantile(RMSE, probs = c(0.75), na.rm = T),
    IQ = q75 - q25
  ) %>%
  arrange(median)


p_sps_sum <- res %>%
  dplyr::filter(grepl("SPS", sensor)) %>%
  dplyr::filter(type == "Full") %>%
  dplyr::filter(dataset_type == "cal") %>%
  ggplot(aes(x = reorder(method, RMSE, median), y = RMSE)) +
  geom_boxplot(
    fatten = 0.8,
    outlier.size = 0.8,
    outlier.alpha = 0.5,
    lwd = 0.2
  ) +
  xlab("Calibration method") +
  ylab(quickText("RMSE (ug/m3)")) +
  scale_y_continuous(labels = scaleFUN, limits = quantile(res$RMSE, c(0.1, 0.9))) +
  custom_theme +
  theme(axis.text.x = element_text(
    angle = 90,
    hjust = 0.95,
    vjust = 0.2
  )) +
  stat_summary(
    geom = "text",
    fun =  ~ quantile(.x, probs = c(1, 2, 3) / 4),
    aes(label = sprintf("%1.1f", ..y..)),
    size = 2.5,
    colour = "sienna"
  )

#p_sps_sum
legend <- get_legend(# create some space to the left of the legend
  p_sps +
    guides(color = guide_legend(ncol = 1, title = "Sensors")) +
    theme(legend.box.margin = margin(0, 0, 0, 0)))





pg <-
  plot_grid(
    p_sps + xlab(NULL) + guides(x = "none") + theme(legend.position = "none"),
    p_sps_sum,
    nrow = 2,
    labels = c("(a)", "(b)"),
    label_y = c(0.1, 0.1)
  )
#pg
pg_l <- plot_grid(pg,
                  legend,
                  ncol = 2,
                  rel_widths  = c(0.8, 0.2))
pg_l
ggsave2(
  plot = pg_l,
  filename = paste0(PLOT_OUTPUT_FOLDER, "2weeks_4days_sps.png"),
  height = 140,
  units = "mm"
)

```


```{r}



p_pms <- res %>%
  dplyr::filter(grepl("PMS", sensor)) %>%
  dplyr::filter(type == "Full") %>%
  dplyr::filter(dataset_type == "cal") %>%
  ggplot(aes(
    x = reorder(method, RMSE, median),
    y = RMSE,
    colour = sensor
  )) +
  stat_boxplot(geom = 'errorbar') +
  geom_boxplot(
    fatten = 0.8,
    outlier.size = 0.8,
    outlier.alpha = 0.5,
    lwd = 0.2
  ) +
  custom_theme +
  xlab("Calibration method") +
  ylab(quickText("RMSE (ug/m3)")) +
  labs(colour = "Sensors") +
  scale_y_continuous(labels = scaleFUN, limits = quantile(res$RMSE, c(0.1, 0.9))) +
  theme(axis.text.x = element_text(
    angle = 90,
    hjust = 0.95,
    vjust = 0.2
  )) 

ggsave2(
  plot = p_pms,
  filename = paste0(PLOT_OUTPUT_FOLDER, "2weeks_4days_pms.png"),
  height = 130,
  units = "mm",
  width = 190
)

#p_pms





res %>%
  dplyr::filter(grepl("PMS", sensor)) %>%
  dplyr::filter(type == "Full") %>%
  dplyr::filter(dataset_type == "cal") %>%
  group_by(method) %>%
  summarise(
    mean  = mean(RMSE, na.rm = T),
    median  = median(RMSE, na.rm = T),
    q25 = quantile(RMSE, probs = c(0.25), na.rm = T),
    q75  = quantile(RMSE, probs = c(0.75), na.rm = T),
    IQ = q75 - q25
  )




p_pms_sum <- res %>%
  dplyr::filter(grepl("PMS", sensor)) %>%
  dplyr::filter(type == "Full") %>%
  dplyr::filter(dataset_type == "cal") %>%
  ggplot(aes(x = reorder(method, RMSE, median), y = RMSE)) +
  stat_boxplot(geom = 'errorbar', width = 0.5, size = 0.1) +
  geom_boxplot(
    fatten = 0.8,
    outlier.size = 0.8,
    outlier.alpha = 0.5,
    lwd = 0.2
  ) +
  xlab("Calibration method") +
  ylab(quickText("RMSE (ug/m3)")) +
  custom_theme +
  scale_y_continuous(labels = scaleFUN, limits = quantile(res$RMSE, c(0.1, 0.9))) +
  theme(axis.text.x = element_text(
    angle = 90,
    hjust = 0.95,
    vjust = 0.2
  )) +
  stat_summary(
    geom = "text",
    fun =  ~ quantile(.x, probs = c(1, 2, 3) / 4),
    aes(label = sprintf("%1.1f", ..y..)),
    size = 2.5,
    colour = "sienna"
  )



legend <- get_legend(# create some space to the left of the legend
  p_pms +
    guides(color = guide_legend(ncol = 1, title = "Sensors")) +
    #theme(legend.position = "bottom") +
    theme(legend.box.margin = margin(0, 0, 0, 0)))




pg <-
  plot_grid(
    p_pms + xlab(NULL) + guides(x = "none") + theme(legend.position = "none"),
    p_pms_sum,
    nrow = 2,
    labels = c("(a)", "(b)"),
    label_y = c(0.1, 0.1)
  )
#pg
pg_l <- plot_grid(pg,
                  legend,
                  ncol = 2,
                  rel_widths  = c(0.8, 0.2))
pg_l

ggsave2(
  plot = pg_l,
  filename = paste0(PLOT_OUTPUT_FOLDER, "2weeks_4days_pms.png"),
  height = 140,
  units = "mm"
)


```






# Expanded uncertainty

```{r}



p_sps <- res %>%
  dplyr::filter(grepl("SPS", sensor)) %>%
  dplyr::filter(type == "Full") %>%
  dplyr::filter(dataset_type == "cal") %>%
  ggplot(aes(x = method, y = expanded_uncertainty*100, colour = sensor)) +
  stat_boxplot(geom = 'errorbar') +
  geom_boxplot(
    fatten = 0.8,
    outlier.size = 0.8,
    outlier.alpha = 0.5,
    lwd = 0.2
  ) +
  custom_theme +
  xlab("Calibration method") +
  ylab(quickText("expanded_uncertainty (%)")) +
  labs(colour = "Sensors") +
  scale_y_continuous(labels = scaleFUN,
                     limits = quantile(res$expanded_uncertainty*100, c(0.1, 0.9), na.rm = T)) +
  theme(axis.text.x = element_text(
    angle = 90,
    hjust = 0.95,
    vjust = 0.2
  )) 
#p_sps

res %>%
  dplyr::filter(grepl("SPS", sensor)) %>%
  dplyr::filter(type == "Full") %>%
  dplyr::filter(dataset_type == "cal") %>%
  group_by(method) %>%
  summarise(
    mean  = mean(expanded_uncertainty, na.rm = T),
    median  = median(expanded_uncertainty, na.rm = T),
    q25 = quantile(
      expanded_uncertainty,
      probs = c(0.25),
      na.rm = T
    ),
    q75  = quantile(
      expanded_uncertainty,
      probs = c(0.75),
      na.rm = T
    ),
    IQ = q75 - q25
  )


p_sps_sum <- res %>%
  dplyr::filter(grepl("SPS", sensor)) %>%
  dplyr::filter(type == "Full") %>%
  dplyr::filter(dataset_type == "cal") %>%
  ggplot(aes(x = method, y = expanded_uncertainty*100)) +
  stat_boxplot(geom = 'errorbar') +
  geom_boxplot(
    fatten = 0.8,
    outlier.size = 0.8,
    outlier.alpha = 0.5,
    lwd = 0.2
  ) +
  xlab("Calibration method") +
  ylab(quickText("expanded_uncertainty (%)")) +
  scale_y_continuous(labels = scaleFUN,
                     limits = quantile(res$expanded_uncertainty*100, c(0.1, 0.9), na.rm = T)) +
  custom_theme +
  theme(axis.text.x = element_text(
    angle = 90,
    hjust = 0.95,
    vjust = 0.2
  ))


legend <- get_legend(# create some space to the left of the legend
  p_sps +
    guides(color = guide_legend(ncol = 1, title = "Sensors")) +
    #theme(legend.position = "bottom") +
    theme(legend.box.margin = margin(0, 0, 0, 0)))





pg <-
  plot_grid(
    p_sps + xlab(NULL) + guides(x = "none") + theme(legend.position = "none"),
    p_sps_sum,
    nrow = 2,
    labels = c("(a)", "(b)"),
    label_y = c(0.1, 0.1)
  )
#pg
pg_l <- plot_grid(pg,
                  legend,
                  ncol = 2,
                  rel_widths  = c(0.8, 0.2))
pg_l
ggsave2(
  plot = pg_l,
  filename = paste0(PLOT_OUTPUT_FOLDER, "2weeks_40days_exp_uncertainty_sps.png"),
  height = 140,
  units = "mm"
)


```


```{r}



p_pms <- res %>%
  dplyr::filter(grepl("PMS", sensor)) %>%
  dplyr::filter(type == "Full") %>%
  dplyr::filter(dataset_type == "cal") %>%
  ggplot(aes(x = method, y = expanded_uncertainty*100, colour = sensor)) +
  stat_boxplot(geom = 'errorbar') +
  geom_boxplot(
    fatten = 0.8,
    outlier.size = 0.8,
    outlier.alpha = 0.5,
    lwd = 0.2
  ) +
  custom_theme +
  xlab("Calibration method") +
  ylab(quickText("expanded_uncertainty (%)")) +
  labs(colour = "Sensors") +
  scale_y_continuous(labels = scaleFUN,
                     limits = quantile(res$expanded_uncertainty*100, c(0.1, 0.9), na.rm = T)) +
  theme(axis.text.x = element_text(
    angle = 90,
    hjust = 0.95,
    vjust = 0.2
  )) #+
#facet_wrap(~sensor_type,nrow=1,scales="free")
#ggsave2(plot = p_pms,filename=paste0(PLOT_OUTPUT_FOLDER, "2weeks_40days_exp_uncertainty_pms.png"),
#       height = 130, units = "mm",width = 190)
#reorder(method,expanded_uncertainty,na.rm=T,median)
p_pms

#



res %>%
  dplyr::filter(grepl("PMS", sensor)) %>%
  dplyr::filter(type == "Full") %>%
  dplyr::filter(dataset_type == "cal") %>%
  group_by(method) %>%
  summarise(
    mean  = mean(expanded_uncertainty, na.rm = T),
    median  = median(expanded_uncertainty, na.rm = T),
    q25 = quantile(
      expanded_uncertainty,
      probs = c(0.25),
      na.rm = T
    ),
    q75  = quantile(
      expanded_uncertainty,
      probs = c(0.75),
      na.rm = T
    ),
    IQ = q75 - q25
  )




p_pms_sum <- res %>%
  dplyr::filter(grepl("PMS", sensor)) %>%
  dplyr::filter(type == "Full") %>%
  dplyr::filter(dataset_type == "cal") %>%
  ggplot(aes(x = reorder(method, expanded_uncertainty), y = expanded_uncertainty*100)) +
  stat_boxplot(geom = 'errorbar', width = 0.5, size = 0.1) +
  geom_boxplot(
    fatten = 0.8,
    outlier.size = 0.8,
    outlier.alpha = 0.5,
    lwd = 0.2
  ) +
  xlab("Calibration method") +
  ylab(quickText("expanded_uncertainty (%)")) +
  custom_theme +
  scale_y_continuous(labels = scaleFUN,
                     limits = quantile(res$expanded_uncertainty*100, c(0.1, 0.9), na.rm = T)) +
  theme(axis.text.x = element_text(
    angle = 90,
    hjust = 0.95,
    vjust = 0.2
  )) #+
#facet_wrap(~scenario_type,nrow=2,scales="free")


legend <- get_legend(# create some space to the left of the legend
  p_pms +
    guides(color = guide_legend(ncol = 1, title = "Sensors")) +
    #theme(legend.position = "bottom") +
    theme(legend.box.margin = margin(0, 0, 0, 0)))




pg <-
  plot_grid(
    p_pms + xlab(NULL) + guides(x = "none") + theme(legend.position = "none"),
    p_pms_sum,
    nrow = 2,
    labels = c("(a)", "(b)"),
    label_y = c(0.1, 0.1)
  )
pg
pg_l <- plot_grid(pg,
                  legend,
                  ncol = 2,
                  rel_widths  = c(0.8, 0.2))
pg_l

ggsave2(
  plot = pg_l,
  filename = paste0(PLOT_OUTPUT_FOLDER, "2weeks_40days_exp_uncertainty_pms.png"),
  height = 140,
  units = "mm"
)


```

# Between unit uncertainty


```{r}





p_sps_sum <- res_bus %>%
  dplyr::filter(type == "Full") %>%
  dplyr::filter(grepl("SPS", combination)) %>%
  dplyr::filter(dataset_type == "cal") %>%
  ggplot(aes(x = method, y = usb)) +
  stat_boxplot(geom = 'errorbar') +
  #geom_violin(fatten=0.8,outlier.size = 0.8,outlier.alpha=0.5,lwd=0.2) +
  geom_boxplot(
    atten = 0.8,
    outlier.size = 0.8,
    outlier.alpha = 0.5,
    lwd = 0.2
  ) +
  xlab("Calibration method") +
  ylab(quickText("Between unit-uncertainty (ug/m3)")) +
  scale_y_continuous(labels = scaleFUN,
                     limits = quantile(res_bus$usb, c(0.1, 0.9), na.rm = T)) +
    ggtitle(label = "SPS") +
  custom_theme +
  theme(axis.text.x = element_text(
    angle = 90,
    hjust = 0.95,
    vjust = 0.2
  ))
p_sps_sum


p_pms_sum <- res_bus %>%
  dplyr::filter(type == "Full") %>%
  dplyr::filter(grepl("PMS", combination)) %>%
  dplyr::filter(dataset_type == "cal") %>%
  ggplot(aes(x = method, y = usb)) +
  stat_boxplot(geom = 'errorbar') +
  geom_violin(
    fatten = 0.8,
    outlier.size = 0.8,
    outlier.alpha = 0.5,
    lwd = 0.2
  ) +
  geom_boxplot(
    fatten = 0.8,
    outlier.size = 0.8,
    outlier.alpha = 0.5,
    lwd = 0.2
  ) +
  xlab("Calibration method") +
  ylab(quickText("Between unit-uncertainty (ug/m3)")) +
    ggtitle(label = "PMS") +
  scale_y_continuous(labels = scaleFUN,
                     limits = quantile(res_bus$usb, c(0.1, 0.9), na.rm = T)) +
  custom_theme +
  theme(axis.text.x = element_text(
    angle = 90,
    hjust = 0.95,
    vjust = 0.2
  ))
p_pms_sum


```


# Coefficient of variation

```{r}


p_sps_sum <- res %>%
  dplyr::filter(type == "Full") %>%
  dplyr::filter(grepl("SPS", sensor)) %>%
  dplyr::filter(dataset_type == "cal") %>%
  ggplot(aes(x = method, y = cv)) +
  stat_boxplot(geom = 'errorbar') +
  geom_violin(
    fatten = 0.8,
    outlier.size = 0.8,
    outlier.alpha = 0.5,
    lwd = 0.2
  ) +
  geom_boxplot(width = 0.1) +
  xlab("Calibration method") +
  ylab(quickText("CV")) +
    ggtitle(label = "SPS") +
  scale_y_continuous(labels = scaleFUN, limits = quantile(res$cv, c(0.1, 0.9), na.rm =
                                                            T)) +
  custom_theme +
  theme(axis.text.x = element_text(
    angle = 90,
    hjust = 0.95,
    vjust = 0.2
  ))
p_sps_sum


p_pms_sum <- res %>%
  dplyr::filter(type == "Full") %>%
  dplyr::filter(grepl("PMS", sensor)) %>%
  dplyr::filter(dataset_type == "cal") %>%
  ggplot(aes(x = method, y = cv)) +
  stat_boxplot(geom = 'errorbar') +
  geom_violin(
    fatten = 0.8,
    outlier.size = 0.8,
    outlier.alpha = 0.5,
    lwd = 0.2
  ) +
  geom_boxplot(width = 0.1) +
  xlab("Calibration method") +
  ylab(quickText("CV")) +
  ggtitle(label = "PMS") +
  scale_y_continuous(labels = scaleFUN, limits = quantile(res$cv, c(0.1, 0.9), na.rm =
                                                            T)) +
  custom_theme +
  theme(axis.text.x = element_text(
    angle = 90,
    hjust = 0.95,
    vjust = 0.2
  ))
p_pms_sum


```

