---
title: "Demonstration of equivalence for different time averages and comparison"
author: "FMJ Bulot"
date: "`r format(Sys.time(), '%d %B, %Y, %H:%M')`"
output:
  html_document:
    df_print: paged
    code_folding: hide
    toc: true
    toc_depth: 2
    toc_float:
      collapsed: false
knit: (function(inputFile, encoding) { 
      out_dir <- '../docs/';
      rmarkdown::render(inputFile,
                        encoding=encoding, 
                        output_file=file.path(dirname(inputFile), out_dir, 'demo_equivalence_avg.html'))})
editor_options: 
  markdown: 
    wrap: 80
---

```{r global_options, include=FALSE}
knitr::opts_chunk$set(fig.width=12, fig.height=8, fig.path='../Figs/demo_equivalence_avg/',warning=FALSE, message=FALSE)
```

This notebook presents the time series of the data recorded by the
sensors during the duration of the NOCS study. In this notebook, we
check whether the sensors match the criteria for the demonstration of
equivalence at different time resolution.

Results are calculated in a separate script,  
`demo_equivalence/demo_equivalence_avg.r`, as they are long to compute. 
They are stored in `output/demo_equivalence_avg.r`

```{r setup, message=F}
require(stringr)

source("utilities/utilities.R")
source("utilities/nested_models.r")
source("utilities/variables.r")

input_folder <- paste0(here::here(), "/output/demo_equivalence_avg/")

```

# Impact of the time averaging on the metrics  {.tabset .tabset-pills}

```{r}
res_2min <- readRDS(paste0(input_folder, "res_2min_dates.rds"))

res_2min_ue <- lapply(res_2min, function(x)
  bind_rows(x$res)) %>%
  bind_rows
res_2min_bus <-
  lapply(res_2min, function(x)
    bind_rows(x$res_bus)) %>%
  bind_rows

res_1h <- readRDS(paste0(input_folder, "res_1h_dates.rds"))

res_1h_ue <- lapply(res_1h, function(x)
  bind_rows(x$res)) %>%
  bind_rows
res_1h_bus <- lapply(res_1h, function(x)
  bind_rows(x$res_bus)) %>%
  bind_rows

res_1d <- readRDS(paste0(input_folder, "res_1day_dates.rds"))

res_1d_ue <- lapply(res_1d, function(x)
  bind_rows(x$res)) %>%
  bind_rows
res_1d_bus <- lapply(res_1d, function(x)
  bind_rows(x$res_bus)) %>%
  bind_rows

res_bind_ue <- res_1h_ue %>%
  bind_rows(res_1d_ue) %>%
  bind_rows(res_2min_ue) %>%
  dplyr::filter(!grepl("N2", sensor)) %>%
  dplyr::mutate(expanded_uncertainty = expanded_uncertainty * 100) %>%
  mutate(sensor_type = ifelse(grepl("SPS", sensor), "SPS30", "PMS5003"))

res_bind_bus <- res_1h_bus %>%
  bind_rows(res_1d_bus) %>%
  bind_rows(res_2min_bus) %>%
  dplyr::filter(!grepl("N2", combination)) %>%
  dplyr::filter(!(grepl("SPS", combination) &
                    grepl("PMS", combination))) %>%
  mutate(sensor_type = ifelse(grepl("SPS", combination), "SPS30", "PMS5003"))

```

## Expanded uncertainty

```{r, echo=FALSE}

p <- res_bind_ue %>%
  dplyr::filter(type == "Full") %>%
  ggplot(aes(y = expanded_uncertainty, x = sensor, colour = method)) +
  stat_boxplot(geom = 'errorbar') +
  geom_boxplot(fatten = 0.8,
               outlier.size = 0.8,
               outlier.alpha = 0.5) +
  geom_hline(yintercept = 50, linetype = 3) +
  ylab(quickText("Expanded uncertainty (%)")) +
  custom_theme +
  facet_wrap( ~ sensor_type, scales = "free", ncol = 1) +
  theme(axis.text.x = element_text(
    angle = 45,
    vjust = 1,
    hjust = 1
  ))
p

res_bind_ue %>%
  dplyr::filter(type == "Full") %>%
  group_by(sensor_type, method) %>%
  summarise(
    max(expanded_uncertainty, na.rm = T),
    min(expanded_uncertainty, na.rm = T),
    quant25 = quantile(
      expanded_uncertainty,
      probs = c(0.25),
      na.rm = T
    ),
    quant75 = quantile(
      expanded_uncertainty,
      probs = c(0.75),
      na.rm = T
    ),
    median(expanded_uncertainty, na.rm = T)
  )

```

### Plot with significance levels

We conduct a shapiro test to test the normality assumption on the expanded 
uncertainty and a Levene test to test the assumption 
that variances are homogeneous.

#### Shapiro test
```{r}


res_bind_ue %>%
  dplyr::filter(type == "Full") %>%
  group_by(sensor, sensor_type, method) %>%
  shapiro_test(expanded_uncertainty)
```

#### Levene test

```{r}
res_bind_ue %>%
  dplyr::filter(type == "Full") %>%
  na.exclude() %>%
  dplyr::filter(sensor_type == "PMS5003") %>%
  group_by(sensor) %>%
  levene_test(expanded_uncertainty ~ method)

res_bind_ue %>%
  dplyr::filter(type == "Full") %>%
  na.exclude() %>%
  dplyr::filter(sensor_type == "SPS30") %>%
  group_by(sensor) %>%
  levene_test(expanded_uncertainty ~ method)


```

The data are not different from a normal distribution. The variances are
homogeneous for the SPS but not for some of the PMS.

```{r}

stat.test_pms <- res_bind_ue %>%
  dplyr::filter(type == "Full") %>%
  dplyr::filter(sensor_type == "PMS5003") %>%
  na.exclude() %>%
  group_by(sensor, sensor_type) %>%
  t_test(expanded_uncertainty ~ method, var.equal = FALSE) %>%
  add_significance()

stat.test_pms <- stat.test_pms %>%
  add_xy_position(x = "sensor", dodge = 0.8)


p_pms <- res_bind_ue %>%
  dplyr::filter(type == "Full") %>%
  dplyr::filter(sensor_type == "PMS5003") %>%
  ggplot(aes(y = expanded_uncertainty, x = sensor, colour = method)) +
  stat_boxplot(geom = 'errorbar') +
  geom_boxplot(fatten = 0.8,
               outlier.size = 0.8,
               outlier.alpha = 0.5) +
  geom_hline(yintercept = 50, linetype = 3) +
  ylab(quickText("Expanded uncertainty (%)")) +
  custom_theme +
  facet_wrap( ~ sensor_type, scales = "free") +
  theme(axis.text.x = element_text(
    angle = 45,
    vjust = 1,
    hjust = 1
  ))
#p_pms

p_pms <- p_pms + stat_pvalue_manual(
  stat.test_pms,
  label = "p.adj.signif",
  tip.length = 0.01,
  bracket.nudge.y = 0,
  hide.ns = T
) +
  scale_y_continuous(expand = expansion(mult = c(0.01, 0.1)))

p_sps <- res_bind_ue %>%
  dplyr::filter(type == "Full") %>%
  dplyr::filter(sensor_type == "SPS30") %>%
  ggplot(aes(y = expanded_uncertainty, x = sensor, colour = method)) +
  stat_boxplot(geom = 'errorbar') +
  geom_boxplot(fatten = 0.8,
               outlier.size = 0.8,
               outlier.alpha = 0.5) +
  geom_hline(yintercept = 50, linetype = 3) +
  ylab(quickText("Expanded uncertainty (%)")) +
  xlab("Sensors") +
  custom_theme +
  facet_wrap( ~ sensor_type, scales = "free") +
  theme(axis.text.x = element_text(
    angle = 45,
    vjust = 1,
    hjust = 1
  ))

stat.test_sps <- res_bind_ue %>%
  dplyr::filter(type == "Full") %>%
  dplyr::filter(sensor_type == "SPS30") %>%
  na.exclude() %>%
  group_by(sensor, sensor_type) %>%
  t_test(expanded_uncertainty ~ method) %>%
  add_significance()

stat.test_sps <- stat.test_sps %>%
  add_xy_position(x = "sensor", dodge = 0.8)

p_sps <- p_sps + stat_pvalue_manual(
  stat.test_sps,
  label = "p.adj.signif",
  tip.length = 0.01,
  bracket.nudge.y = 0,
  hide.ns = T
) +
  scale_y_continuous(expand = expansion(mult = c(0.01, 0.1)))
#p_sps
#https://www.datanovia.com/en/blog/how-to-add-p-values-onto-a-grouped-ggplot-using-the-ggpubr-r-package/


p <- plot_grid(p_pms + xlab(NULL),
               p_sps,
               nrow = 2)
p
p %>%
  ggsave2(
    filename = paste0(PLOT_OUTPUT_FOLDER, "demo_equivalence_avg.svg"),
    height = 140,
    units = "mm"
  )

```

## Between unit uncertainty

```{r, echo=FALSE}


p <- res_bind_bus %>%
  dplyr::filter(type == "Full") %>%
  ggplot(aes(
    x = reorder(str_remove_all(combination, "SPS-|PMS-"), usb),
    y = usb,
    colour = method
  )) +
  stat_boxplot(geom = 'errorbar') +
  geom_boxplot(fatten = 0.8,
               outlier.size = 0.8,
               outlier.alpha = 0.5) +
  custom_theme +
  theme(axis.text.x = element_text(
    angle = 90,
    hjust = 0.95,
    vjust = 0.2
  )) +
  ylab(quickText("Between unit uncertainty (ug/m3)")) +
  xlab("Combinations") +
  facet_wrap( ~ sensor_type, scales = "free_x", ncol = 1) +
  theme(axis.text.x = element_text(
    angle = 45,
    vjust = 1,
    hjust = 1
  ))

p

res_bind_bus %>%
  dplyr::filter(type == "Full") %>%
  group_by(sensor_type, method) %>%
  summarise(
    max(usb, na.rm = T),
    min(usb, na.rm = T),
    quant25 = quantile(usb, probs = c(0.25), na.rm = T),
    quant75 = quantile(usb, probs = c(0.75), na.rm = T),
    median(usb, na.rm = T)
  )

```

### Plot with significance levels

#### Shapiro test

```{r}


res_bind_bus %>%
  dplyr::filter(type == "Full") %>%
  group_by(combination, sensor_type, method) %>%
  shapiro_test(usb)
```

#### Levene test

```{r}
res_bind_bus %>%
  dplyr::filter(type == "Full") %>%
  na.exclude() %>%
  dplyr::filter(sensor_type == "PMS5003") %>%
  group_by(combination) %>%
  levene_test(usb ~ method)

res_bind_bus %>%
  dplyr::filter(type == "Full") %>%
  na.exclude() %>%
  dplyr::filter(sensor_type == "SPS30") %>%
  group_by(combination) %>%
  levene_test(usb ~ method)

```

The groups are all normal. The PMS combination does not all have
homogeneous variances.

```{r}

stat.test_pms <- res_bind_bus  %>%
  dplyr::filter(type == "Full") %>%
  dplyr::filter(sensor_type == "PMS5003") %>%
  na.exclude() %>%
  group_by(combination, sensor_type) %>%
  t_test(usb ~ method, var.equal = FALSE) %>%
  add_significance()

stat.test_pms <- stat.test_pms %>%
  add_xy_position(x = "combination", dodge = 0.8)


p_pms <- res_bind_bus %>%
  dplyr::filter(type == "Full") %>%
  dplyr::filter(sensor_type == "PMS5003") %>%
  ggplot(aes(
    x = str_remove_all(combination, "SPS-|PMS-"),
    y = usb,
    colour = method
  )) +
  stat_boxplot(geom = 'errorbar') +
  geom_boxplot(fatten = 0.8,
               outlier.size = 0.8,
               outlier.alpha = 0.5) +
  custom_theme +
  theme(axis.text.x = element_text(
    angle = 90,
    hjust = 0.95,
    vjust = 0.2
  )) +
  ylab(quickText("Between unit uncertainty (ug/m3)")) +
  xlab("Combinations") +
  facet_wrap( ~ sensor_type, scales = "free_x", ncol = 1) +
  theme(axis.text.x = element_text(
    angle = 45,
    vjust = 1,
    hjust = 1
  ))
#

p_pms <- p_pms + stat_pvalue_manual(
  stat.test_pms,
  label = "p.adj.signif",
  tip.length = 0.01,
  bracket.nudge.y = 0,
  hide.ns = T
) +
  scale_y_continuous(expand = expansion(mult = c(0.01, 0.1)))

p_sps <- res_bind_bus %>%
  dplyr::filter(type == "Full") %>%
  dplyr::filter(sensor_type == "SPS30") %>%
  ggplot(aes(
    x = str_remove_all(combination, "SPS-|PMS-"),
    y = usb,
    colour = method
  )) +
  stat_boxplot(geom = 'errorbar') +
  geom_boxplot(fatten = 0.8,
               outlier.size = 0.8,
               outlier.alpha = 0.5) +
  custom_theme +
  theme(axis.text.x = element_text(
    angle = 90,
    hjust = 0.95,
    vjust = 0.2
  )) +
  ylab(quickText("Between unit uncertainty (ug/m3)")) +
  xlab("Combinations") +
  facet_wrap( ~ sensor_type, scales = "free_x", ncol = 1) +
  theme(axis.text.x = element_text(
    angle = 45,
    vjust = 1,
    hjust = 1
  ))

stat.test_sps <- res_bind_bus  %>%
  dplyr::filter(type == "Full") %>%
  dplyr::filter(sensor_type == "SPS30") %>%
  na.exclude() %>%
  group_by(combination, sensor_type) %>%
  t_test(usb ~ method, var.equal = TRUE) %>%
  add_significance()

stat.test_sps <- stat.test_sps %>%
  add_xy_position(x = "combination", dodge = 0.8)

p_sps <- p_sps + stat_pvalue_manual(
  stat.test_sps,
  label = "p.adj.signif",
  tip.length = 0.01,
  bracket.nudge.y = 0,
  hide.ns = T
) +
  scale_y_continuous(expand = expansion(mult = c(0.01, 0.1)))
#p_sps

p <- plot_grid(p_pms + xlab(NULL),
               p_sps,
               nrow = 2)

p %>%
  ggsave2(
    filename = paste0(PLOT_OUTPUT_FOLDER, "demo_equivalence_avg_buu.svg"),
    height = 140,
    units = "mm"
  )
p
```

## U

```{r}


equivalence_avg_comparison <- function(res_bind_ue, title, field) {
  p_pms <- res_bind_ue %>%
    dplyr::filter(type == "Full") %>%
    ggplot(aes(y = .data[[field]], x = sensor, colour = method)) +
    stat_boxplot(geom = 'errorbar') +
    geom_boxplot(fatten = 0.8,
                 outlier.size = 0.8,
                 outlier.alpha = 0.5) +
    ylab(quickText(title)) +
    custom_theme +
    facet_wrap( ~ sensor_type, scales = "free", ncol = 1) +
    theme(axis.text.x = element_text(
      angle = 45,
      vjust = 1,
      hjust = 1
    ))
  p_pms
  
  
}

equivalence_avg_comparison(res_bind_ue, title = "Expanded uncertainty USEPA (%)", field = "U")
equivalence_avg_comparison(res_bind_ue, title = "RMSE (ug/m3)", field = "RMSE")
equivalence_avg_comparison(res_bind_ue, title = "CV (%)", field = "cv")
equivalence_avg_comparison(res_bind_ue, title = "R2", field = "r2")
equivalence_avg_comparison(res_bind_ue, title = "Bias (ug/m3)", field = "y__")

```

## RMSE

```{r}


equivalence_avg_comparison(res_bind_ue, title = "RMSE (ug/m3)", field = "RMSE") %>%
  ggsave2(
    filename = paste0(PLOT_OUTPUT_FOLDER, "demo_equivalence_avg_RMSE.png"),
    height = 140,
    units = "mm"
  )

res_bind_ue %>%
  dplyr::filter(type == "Full") %>%
  group_by(sensor_type, method) %>%
  summarise(
    max(RMSE, na.rm = T),
    min(RMSE, na.rm = T),
    quant25 = quantile(RMSE, probs = c(0.25), na.rm = T),
    quant75 = quantile(RMSE, probs = c(0.75), na.rm = T),
    median(RMSE, na.rm = T)
  )

```

### Plot with significance levels

#### Shapiro test

```{r}


res_bind_ue %>%
  dplyr::filter(type == "Full") %>%
  group_by(sensor, sensor_type, method) %>%
  shapiro_test(RMSE)
```


#### Levene test

```{r}
res_bind_ue %>%
  dplyr::filter(type == "Full") %>%
  na.exclude() %>%
  dplyr::filter(sensor_type == "PMS5003") %>%
  group_by(sensor) %>%
  levene_test(RMSE ~ method)

res_bind_ue %>%
  dplyr::filter(type == "Full") %>%
  na.exclude() %>%
  dplyr::filter(sensor_type == "SPS30") %>%
  group_by(sensor) %>%
  levene_test(RMSE ~ method)

```

The data are not different from a normal distribution. The variances are
homogeneous for both models of sensors.

```{r}

stat.test_pms <- res_bind_ue %>%
  dplyr::filter(type == "Full") %>%
  dplyr::filter(sensor_type == "PMS5003") %>%
  na.exclude() %>%
  group_by(sensor, sensor_type) %>%
  t_test(RMSE ~ method, var.equal = TRUE) %>%
  add_significance()

stat.test_pms <- stat.test_pms %>%
  add_xy_position(x = "sensor", dodge = 0.8)

p_pms <- res_bind_ue %>%
  dplyr::filter(type == "Full") %>%
  dplyr::filter(sensor_type == "PMS5003") %>%
  ggplot(aes(y = RMSE, x = sensor, colour = method)) +
  stat_boxplot(geom = 'errorbar') +
  geom_boxplot(fatten = 0.8,
               outlier.size = 0.8,
               outlier.alpha = 0.5) +
  ylab(quickText("RMSE (ug/m3)")) +
  custom_theme +
  facet_wrap(~ sensor_type, scales = "free") +
  theme(axis.text.x = element_text(
    angle = 45,
    vjust = 1,
    hjust = 1
  ))
#p_pms

p_pms <- p_pms + stat_pvalue_manual(
  stat.test_pms,
  label = "p.adj.signif",
  tip.length = 0.01,
  bracket.nudge.y = 0,
  hide.ns = T
) +
  scale_y_continuous(expand = expansion(mult = c(0.01, 0.1)))

p_sps <- res_bind_ue %>%
  dplyr::filter(type == "Full") %>%
  dplyr::filter(sensor_type == "SPS30") %>%
  ggplot(aes(y = RMSE, x = sensor, colour = method)) +
  stat_boxplot(geom = 'errorbar') +
  geom_boxplot(fatten = 0.8,
               outlier.size = 0.8,
               outlier.alpha = 0.5) +
  ylab(quickText("RMSE (ug/m3)")) +
  custom_theme +
  facet_wrap(~ sensor_type, scales = "free") +
  theme(axis.text.x = element_text(
    angle = 45,
    vjust = 1,
    hjust = 1
  ))

stat.test_sps <- res_bind_ue %>%
  dplyr::filter(type == "Full") %>%
  dplyr::filter(sensor_type == "SPS30") %>%
  na.exclude() %>%
  group_by(sensor, sensor_type) %>%
  t_test(RMSE ~ method) %>%
  add_significance()

stat.test_sps <- stat.test_sps %>%
  add_xy_position(x = "sensor", dodge = 0.8)

p_sps <- p_sps + stat_pvalue_manual(
  stat.test_sps,
  label = "p.adj.signif",
  tip.length = 0.01,
  bracket.nudge.y = 0,
  hide.ns = T
) +
  scale_y_continuous(expand = expansion(mult = c(0.01, 0.1)))
p_sps
#https://www.datanovia.com/en/blog/how-to-add-p-values-onto-a-grouped-ggplot-using-the-ggpubr-r-package/

p <- plot_grid(p_pms + xlab(NULL),
               p_sps,
               nrow = 2)
p %>%
  ggsave2(
    filename = paste0(PLOT_OUTPUT_FOLDER, "demo_equivalence_avg_RMSE.svg"),
    height = 140,
    units = "mm"
  )

p
```