---
title: "Calibration results"
author: "FMJ Bulot"
date: "`r format(Sys.time(), '%d %B, %Y, %H:%M')`"
output:
  html_document:
    df_print: paged
    code_folding: hide
    toc: true
    toc_depth: 2
    toc_float:
      collapsed: false
knit: (function(inputFile, encoding) { 
      out_dir <- '../docs';
      rmarkdown::render(inputFile,
                        encoding=encoding, 
                        output_file=file.path(dirname(inputFile), out_dir, 'test_calibration.html'))})
editor_options: 
  markdown: 
    wrap: 80
---

```{r global_options, include=FALSE}
knitr::opts_chunk$set(fig.width=12, fig.height=8, fig.path='../Figs/test_calibration.html/',warning=FALSE, message=FALSE)
```


The calibration is first tested by using the first two weeks of the data and 
using the next 40 days for verification as described in the 
Supplementary information of the paper.

The results have been calculated by the scripts `test_calibration.r` 
and `test_calibration_ml.r` given the computational time required. The results
are stored in `output/calibration/test_2weeks/`.



```{r}

source("utilities/utilities.R")
source("utilities/nested_models.r")
source("utilities/variables.r")

input_folder <- "../output/calibration/test_2weeks/"

```


# Data preparation

```{r}
file_list <-
  list.files(
    path = input_folder,
    pattern = "res_.*",
    full.names = T,
    recursive = T
  )

# Parse the result files.
res <- data.frame()
res_bus <- data.frame()
for (file in file_list) {
  name <- strsplit(file, "/")[[1]][5]
  scenario <- sub(".rds", "", strsplit(name, "_")[[1]][[5]])
  method <- strsplit(name, "_")[[1]][[2]]
  dataset_type <- strsplit(name, "_")[[1]][[3]]
  tmp <- readRDS(file)
  model <- tmp$res
  model$scenario <- scenario
  model$dataset_type <- dataset_type
  res <- bind_rows(res, model)
  
  model <- tmp$res_bus
  model$scenario <- scenario
  model$dataset_type <- dataset_type
  res_bus <- bind_rows(res_bus, model)
}

res <- res %>%
  mutate(method = str_split(method, " ", simplify = T)[, 1])
res_bus <- res_bus %>%
  mutate(method = str_split(method, " ", simplify = T)[, 1])

# Format the names of the methods
res$method <-
  fct_recode(
    res$method,
    `GBM` = "gbm",
    `GBM+RH` = "gbmrh",
    `Koehler_mass+LR` = "koehlermasslr",
    `Koehler_mass+OLS` = "koehlermassols",
    `Koehler_size+LR` = "koehlersizelr",
    `Koehler_size+OLS` =  "koehlersizeols",
    `Laulainen+LR` = "laulainenlr",
    `Laulainen+OLS` = "laulainenols",
    `MLR_part.` =  "lmpart",
    `MLR_part.+RH` =   "lmpartrh",
    `LR` = "lr",
    `MLR_RH` = "mlr1" ,
    `OLS` =  "ols",
    `RLM` = "rlmhuber",
    `RLM_part.+RH`  = "rlmpartrh",
    `RLM+RH` = "rlmrh",
    `SVM` = "svm",
    `SVM+RH` = "svmrh",
    `Koehler_mass_RH80` = "koehlermassrh80" ,
    `Koehler_mass_RH80+OLS` = "koehlermassrh80ols",
    `Koehler_size` = "koehlersize",
    `Koehler_size_RH80` = "koehlersizerh80",
    `Koehler_size_RH80+OLS` = "koehlersizerh80ols" ,
    `Laulainen` = "laulainen",
    `SVM_part.` = "svmpart",
    `SVM_part.+RH` = "svmpartrh",
    `GBM_part.` = "gbmpart",
    `GBM_part.+RH` = "gbmpartrh",
    `Koehler_mass` = "koehlermass",
    `RLM_part.` = "rlmpart"
  )

# Order the names of the methods
res$method <- fct_relevel(
  res$method,
  "Initial",
  "OLS",
  "LR",
  "MLR_RH",
  "MLR_part.",
  "MLR_part.+RH",
  "RLM",
  "RLM+RH",
  "RLM_part.",
  "RLM_part.+RH",
  "Koehler_mass",
  "Koehler_mass+LR",
  "Koehler_mass+OLS",
  "Koehler_mass_RH80" ,
  "Koehler_mass_RH80+OLS",
  "Koehler_size",
  "Koehler_size+LR",
  "Koehler_size+OLS",
  "Koehler_size_RH80",
  "Koehler_size_RH80+OLS",
  "Laulainen",
  "Laulainen+LR",
  "Laulainen+OLS",
  "GBM",
  "GBM+RH",
  "GBM_part.",
  "GBM_part.+RH",
  "SVM",
  "SVM+RH",
  "SVM_part.",
  "SVM_part.+RH"
)


res_bus$method <-
  fct_recode(
    res_bus$method,
    `GBM` = "gbm",
    `GBM+RH` = "gbmrh",
    `Koehler_mass+LR` = "koehlermasslr",
    `Koehler_mass+OLS` = "koehlermassols",
    `Koehler_size+LR` = "koehlersizelr",
    `Koehler_size+OLS` =  "koehlersizeols",
    `Laulainen+LR` = "laulainenlr",
    `Laulainen+OLS` = "laulainenols",
    `MLR_part.` =  "lmpart",
    `MLR_part.+RH` =   "lmpartrh",
    `LR` = "lr",
    `MLR_RH` = "mlr1" ,
    `OLS` =  "ols",
    `RLM` = "rlmhuber",
    `RLM_part.+RH`  = "rlmpartrh",
    `RLM+RH` =      "rlmrh",
    `SVM` = "svm",
    `SVM+RH` = "svmrh" ,
    `Koehler_mass_RH80` = "koehlermassrh80" ,
    `Koehler_mass_RH80+OLS` = "koehlermassrh80ols",
    `Koehler_size` = "koehlersize",
    `Koehler_size_RH80` = "koehlersizerh80",
    `Koehler_size_RH80+OLS` = "koehlersizerh80ols" ,
    `Laulainen` = "laulainen",
    `SVM_part.` = "svmpart",
    `SVM_part.+RH` = "svmpartrh",
    `GBM_part.` = "gbmpart",
    `GBM_part.+RH` = "gbmpartrh" ,
    `Koehler_mass` = "koehlermass",
    `RLM_part.` = "rlmpart"
  )


res_bus$method <-
  fct_relevel(
    res_bus$method,
    "Initial",
    "OLS",
    "LR",
    "MLR_RH",
    "MLR_part.",
    "MLR_part.+RH",
    "RLM",
    "RLM+RH",
    "RLM_part.",
    "RLM_part.+RH",
    "Koehler_mass",
    "Koehler_mass+LR",
    "Koehler_mass+OLS",
    "Koehler_mass_RH80" ,
    "Koehler_mass_RH80+OLS",
    "Koehler_size",
    "Koehler_size+LR",
    "Koehler_size+OLS",
    "Koehler_size_RH80",
    "Koehler_size_RH80+OLS",
    "Laulainen",
    "Laulainen+LR",
    "Laulainen+OLS",
    "GBM",
    "GBM+RH",
    "GBM_part.",
    "GBM_part.+RH",
    "SVM",
    "SVM+RH",
    "SVM_part.",
    "SVM_part.+RH"
  )


res$sensor_type <- ifelse(grepl("SPS", res$sensor), "SPS", "PMS")

# remove air quality monitor Nocs-2 that stopped working in the middle of the 
# study
res <- res[!grepl("N2", res$sensor), ]
res_bus <- res_bus[!grepl("N2", res_bus$combination), ]

```

# Results

## All results

```{r}

p <- res %>%
  dplyr::filter(type == "Full") %>%
  dplyr::mutate(dataset_type = ifelse(dataset_type == "train", "Training", "Evaluation")) %>%
  ggplot(aes(x = method, y = RMSE)) +
  stat_boxplot(geom = 'errorbar', width = 0.5, size = 0.1) +
  geom_boxplot(
    fatten = 0.8,
    outlier.size = 0.8,
    outlier.alpha = 0.5,
    lwd = 0.2
  ) +
  custom_theme +
  ylab(quickText("RMSE (ug/m3)")) +
  xlab("Calibration method") +
  theme(axis.text.x = element_text(
    angle = 90,
    hjust = 0.95,
    vjust = 0.2
  )) +
  facet_grid(sensor_type ~ dataset_type, scales = "free_y")
p


```

The machine learning methods worked very well for the training dataset but 
much less so for the calibration datasets.

For the PMS, all methods improved the results compared to the initial state. I 
will not take the >80RH for Koehler corrections as they do not bring improvement
compared to the Koehler correction on the full data.


## RMSE for paper

In this graph, I removed the Koehler correction with RH>80 to simplify the view
given the number of methods involved in the comparison.

```{r}


p <- res %>%
  dplyr::filter(!(
    method %in% c(
      "Koehler_mass",
      "Koehler_size",
      "Laulainen",
      "Koehler_mass+OLS",
      "Koehler_size+OLS",
      "Laulainen+OLS"
    )
  )) %>%
  dplyr::filter(type == "Full") %>%
  dplyr::mutate(dataset_type = ifelse(dataset_type == "train", "Training", "Evaluation")) %>%
  dplyr::filter(!grepl("RH80", method)) %>%
  ggplot(aes(x = method, y = RMSE)) +
  stat_boxplot(geom = 'errorbar', width = 0.5, size = 0.1) +
  geom_boxplot(
    fatten = 0.8,
    outlier.size = 0.8,
    outlier.alpha = 0.5,
    lwd = 0.2
  ) +
  custom_theme +
  ylab(quickText("RMSE (ug/m3)")) +
  xlab("Calibration method") +
  theme(axis.text.x = element_text(
    angle = 90,
    hjust = 0.95,
    vjust = 0.2
  )) +
  # ggtitle("Training") +
  facet_grid(sensor_type ~ dataset_type, scales = "free_y")

p
p %>%
  ggsave2(
    filename = paste0(PLOT_OUTPUT_FOLDER, "test_calibration_rmse.png"),
    height = 140,
    units = "mm"
  )


```

## Between unit uncertainty for paper


```{r}



p <- res_bus %>%
  dplyr::filter(!(
    method %in% c(
      "Koehler_mass",
      "Koehler_size",
      "Laulainen",
      "Koehler_mass+OLS",
      "Koehler_size+OLS",
      "Laulainen+OLS"
    )
  )) %>%
  mutate(sensor_type = ifelse(grepl("SPS", combination), "SPS30", "PMS5003")) %>%
  dplyr::filter(type == "Full") %>%
  dplyr::filter(!grepl("RH80", method)) %>%
  dplyr::mutate(dataset_type = ifelse(dataset_type == "train", "Training", "Evaluation")) %>%
  ggplot(aes(x = method, y = usb)) +
  stat_boxplot(geom = 'errorbar', width = 0.5, size = 0.1) +
  geom_boxplot(
    fatten = 0.8,
    outlier.size = 0.8,
    outlier.alpha = 0.5,
    lwd = 0.2
  ) +
  custom_theme +
  theme(axis.text.x = element_text(
    angle = 90,
    hjust = 0.95,
    vjust = 0.2
  )) +
  xlab("Calibration method") +
  ylab("Between unit uncertainty (ug/m3)") +
  facet_grid(sensor_type ~ dataset_type)
p
p %>%
  ggsave2(
    filename = paste0(PLOT_OUTPUT_FOLDER, "test_calibration_buu.png"),
    height = 140,
    units = "mm"
  )
#ggplotly(p)

```






# Clipping of the Machine Learning methods




## Data preparation

```{r}
file_list <-
  list.files(
    path = input_folder,
    pattern = "df_.*",
    full.names = T,
    recursive = T
  )


#fInitialize data.frames
df_cal_pms <- data.frame()
df_train_pms <- data.frame()
df_cal_sps <- data.frame()
df_train_sps <- data.frame()

file <- file_list[1]

for (file in file_list) {
  tmp <- readRDS(file)
  name <- strsplit(file, "/")[[1]][5]
  if (grepl("initial", name)) {
    next
  }
  if (!grepl("train", name)) {
    #message(file)
    if (grepl("SPS", name)) {
      if (dim(df_cal_sps)[1] == 0) {
       # message("Fist sps cal")
        df_cal_sps <- tmp
      }
      else{
       # message("other sps cal")
        df_cal_sps <-
          inner_join(df_cal_sps, tmp, by = c("date", "sensor"))
      }
    }
    else{
      if (dim(df_cal_pms)[1] == 0) {
       # message("Fist pms cal")
        df_cal_pms <- tmp
      }
      else{
       # message("other pms cal")
        df_cal_pms <-
          inner_join(df_cal_pms, tmp, by = c("date", "sensor"))
      }
    }
  }
  else{
    #message("train")
    if (grepl("SPS", name)) {
      if (dim(df_train_sps)[1] == 0) {
        #message("first sps train")
        df_train_sps <- tmp
      }
      else{
       # message("other sps train")
        df_train_sps <-
          inner_join(df_train_sps, tmp, by = c("date", "sensor"))
      }
    }
    else{
      if (dim(df_train_pms)[1] == 0) {
        df_train_pms <- tmp
      }
      else{
        df_train_pms <-
          inner_join(df_train_pms, tmp, by = c("date", "sensor"))
      }
    }
  }
  
  
}
df_2min <- readRDS(DF_JOINED)

```

## Clipping

```{r}

df_tmp <-
  df_2min[df_2min$sensor == "SPS-21N4" &
            df_2min$date >= as.POSIXct("2020-08-09") &
            df_2min$date <= as.POSIXct("2020-08-14"), ]

df_cal_sps_short <-
  df_cal_sps[df_cal_sps$sensor == "SPS-21N4" &
               df_cal_sps$date >= as.POSIXct("2020-08-09") &
               df_cal_sps$date <= as.POSIXct("2020-08-14"), ] %>%
  pivot_longer(
    cols = starts_with("PM25_corr"),
    names_to = "method",
    values_to = "PM25"
  ) %>%
  dplyr::filter(!grepl("koehler_size", method)) %>%
  dplyr::filter(grepl("gbm|svm", method))

df_cal_sps_short$method <-
  fct_recode(
    df_cal_sps_short$method,
    `GBM+RH` = "PM25_corr_gbm_rh",
    `GBM` = "PM25_corr_gbm",
    `SVM` = "PM25_corr_svm",
    `SVM+RH` = "PM25_corr_svm_rh",
    `GBM_part.` = "PM25_corr_gbm_part",
    `GBM_part.+RH` = "PM25_corr_gbm_part_rh",
    `SVM_part.` = "PM25_corr_svm_part",
    `SVM_part.+RH` = "PM25_corr_svm_part_rh",
    `SVM+RH` = "PM25_corr_svmrh"
  )
df_cal_sps_short$method <-
  fct_relevel(
    df_cal_sps_short$method,
    "GBM",
    "GBM+RH",
    "GBM_part.",
    "GBM_part.+RH",
    "SVM",
    "SVM+RH",
    "SVM_part.",
    "SVM_part.+RH"
  )

p <- df_cal_sps_short %>%
  ggplot() +
  geom_line(aes(x = date, y = PM25, colour = "SPS-21N4 corrected"), size =
              0.1) +
  geom_line(
    data = df_tmp,
    aes(x = date, y = median_PM25, colour = "SPS-21N4 uncorrected"),
    alpha = 0.5,
    size = 0.1
  ) +
  geom_line(
    data = df_tmp,
    aes(x = date, y = PM2.5, colour = "Fidas 200S"),
    alpha = 0.5,
    size = 0.1
  ) +
  custom_theme +
  ylab(quickText("PM2.5 (ug/m3)")) +
  labs(colour = "Instrument") +
  facet_wrap( ~ method, nrow =  2)  +
  theme(axis.text.x = element_text(
    angle = 45,
    vjust = 1,
    hjust = 1
  ))
p
p %>%
  ggsave2(
    filename = paste0(PLOT_OUTPUT_FOLDER, "clipping_machine_learning_sps21.png"),
    height = 150,
    units = "mm"
  )

ggplotly(p, dynamicTicks = T)


```

## Interactive version of expanded uncertainty graphs for training and calibration


```{r}



p <- res %>%
  dplyr::filter(grepl("PMS", sensor)) %>%
  dplyr::filter(type == "Full") %>%
  dplyr::filter(dataset_type == "cal") %>%
  ggplot() +
  geom_boxplot(aes(x = method, y = expanded_uncertainty, colour = method)) +
  custom_theme +
  theme(axis.text.x = element_text(
    angle = 90,
    hjust = 0.95,
    vjust = 0.2
  ))  +
  ggtitle("Calibration")
ggplotly(p, dynamicTicks = T)


p <- res %>%
  
  dplyr::filter(grepl("PMS", sensor)) %>%
  dplyr::filter(type == "Full") %>%
  dplyr::filter(dataset_type == "train") %>%
  ggplot() +
  geom_boxplot(aes(x = method, y = expanded_uncertainty, colour = method)) +
  custom_theme +
  theme(axis.text.x = element_text(
    angle = 90,
    hjust = 0.95,
    vjust = 0.2
  )) +
  ggtitle("Training")
ggplotly(p, dynamicTicks = T)
```




